---
title: "Homework 7"
author: "Junyeong_Shin"
date: "10/5/2021"
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
```

# R Library Preview
Please run the following code to install a few more R libraries for Weeks 10 & 11.

```{r}

# Week 10 libraries
install.packages("BiocManager") # Lets you install bioinformatics packages
BiocManager::install("GEOquery") # Lets you download genomics data from the "Gene Expression Omnibus"

BiocManager::install("limma") # Lets you run differential gene expression analysis

# Week 11 libraries
install.packages("pheatmap") # Draw pretty heatmaps
install.packages("rpart") # Recursive partitioning analysis
install.packages("neuralnet") # Neural network analysis


```


# Problem Set
## Q1 (5 points)

Load in `titanic_data.csv`, which provides details about passengers aboard the
Titanic. Calculate the average age of the passengers in the three classes ("Pclass").
*Then,* use an ANOVA test to estimate whether the three passenger classes
("Pclass") contained similar or differently aged ("Age") passengers. 

```{r}
mean(titanic_data$Pclass == 1 & titanic_data$Age, na.rm = TRUE)
mean(titanic_data$Pclass == 2 & titanic_data$Age, na.rm = TRUE)
mean(titanic_data$Pclass == 3 & titanic_data$Age, na.rm = TRUE)

resANOVA <- aov(Pclass ~ Age, data = titanic_data)
summary(resANOVA)
# There were differently aged passengers

```

## Q2 (5 points)

Make a `table` showing the survival ("Survived") for each class. Which class 
had the highest percentage of survivors? *Then,* use a categorical test to 
estimate whether there were different survival rates
("Survived") among the three classes.


```{r}
table(titanic_data$Survived, titanic_data$Pclass)
# Class 1 had the highest percentage of survivors

chisq.test(titanic_data$Survived, titanic_data$Pclass)
#There were different survival rates

```

## Q3 (5 points)

Load in `heart.csv`.  Build a correlation matrix to identify correlations between
numeric variables (variables with 0/1 values are considered categorical). Which
variables are positively or negatively correlated with each other, with correlation
values above 0.3 (or below -0.3)?  

```{r}

cor(heart[,c(-2,-3,-7,-13)])


# maxhr, oldpeak, and slope one with negative correlation with values below -0.3

```

## Q4 (10 points)

### Part 1 (7 points)
Use logistic regression to see if we can make a model to predict heart disease
("disease") from all other variables.  
Which characteristics are significantly (p < 0.05) associated with higher
heart disease in the model?  Please be specific -- for example, do not just say
age is a significant variable (if it is). Instead, say that older or younger participants
are more likely to have heart disease.

```{r}
head(heart)
logiheart =  glm(disease ~ ., data = heart)
summary(logiheart)

# Males, people with chestpain, High Heart rate have a more likely chance to have heart disease.
```

### Part 2 (3 points)

Then, make one relevant visualization to support your answer from the first part 
of the question. 

```{r}
boxplot(disease ~ sex, data = heart)

```
