---
title: "Homework 6"
author: "JunYeong_Shin"
date: "7/26/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Problem Set
## Q1 (10 points)

For Q1-Q3, you are free to use a base plotting function (first half of class) or ggplot2.

Load in the `HortonGeneralHospital.csv` data set.  This file contains data on the
number of three types of transfers into critical care (Cardio, Resp & Hypo), as
well as the total number of patients entering the Emergency Room that month (Adm).
Analysis of this data was used to convict nurse Ben Geen of intentionally harming 18 patients
over the months of December 2003 to February 2004, for which he is serving a life
prison sentence.  Reanalysis of this data is now being used to attempt to grant 
him a new trial (source: https://archive.ics.uci.edu/ml/datasets/Horton+General+Hospital).
We'll do a small portion of this analysis.

Build the most appropriate type of plot showing the number of respiratory (Resp)
critical care transfers each month over the time period in the file (11/1999 to 5/2011). 
Then calculate the total critical care transfers over each month (Cardio, Resp & Hypo), 
and make a similar plot using the totals.


```{r}

# Hint: If you don't want to create a time series object, use this
#     dat$date <- as.Date(paste0(dat$year, "-", dat$month, "-1"), format = "%Y-%m-%d") 
# to generate a "date" column for your data frame. This arbitrarily 
# sets the "date" to the 1st day of each month, which is fine. Then use this 
# column to help make your plot.
HortonGeneralHospital$date <- as.Date(paste0(HortonGeneralHospital$year, "-", HortonGeneralHospital$month, "-1"), format = "%Y-%m-%d")
ggplot(HortonGeneralHospital,aes(x = date, y = Resp))+geom_point()+xlab("Year")+ylab("Number of respiratory transfer")+facet_wrap(~month)


sum(HortonGeneralHospital$Cardio >0)+ sum(HortonGeneralHospital$Hypo >0) + sum(HortonGeneralHospital$Resp >0) 

#this is the totaltransfer of critical care






```


## Q2 (5 points)

Make a scatterplot of the number of Respiratory transfers to critical care (Resp), vs.
the total number of admissions to ER (Adm). Based on this scatterplot, what 
simple observation can you make about the month when there were 4 respiratory transfers?

```{r}

ggplot(HortonGeneralHospital, aes(x = Resp, y = Adm)) +
  geom_point() +
  facet_wrap(~ month)
     
    #Observation is that the 4 respiratory transfer only happened once in December
     
```


## Q3 (5 points)

Load in `SCMS_Delivery_History_Dataset_20150929.csv`. This supply chain data set 
contains HIV testing and antiretroviral shipment data from USAID 
(source: https://data.world/usaid/supply-chain-shipment-pricing).

The "Sub.Classification" column indicates which type of product was included in 
each shipment.  Make a barplot of the counts of that column to show the distribution
of shipment types (i.e. how many shipments included HIV tests, Adult medication, etc.?).

```{r}
scms = read.csv("~/Week 6/Week6_data/SCMS_Delivery_History_Dataset_20150929.csv")
ggplot(scms,aes(Sub.Classification))+geom_bar()

        
       
```

## Q4 (5 points)

Use the ggplot2 library to make a boxplot showing the distribution of "Pack.Price" across 
the different "Sub.Classification" groups. Try to add something to your code
to make the plot easier to read.

```{r}
ggplot(scms, aes(x = Pack.Price, y = Sub.Classification)) +
  geom_boxplot(fill = "pink")+coord_cartesian(xlim= c(0,100))


```
