---
title: "Homework 5"
author: "Junyeong"
date: "7/19/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Problem Set
## Q1 (5 points)

For this assignment, we will be using `leukemia_simulatedData.csv`, which is an
*entirely made-up data set*. Names, dates, and numbers were randomly generated,
and we're pretending that they're PHI for educational purposes.

`leukemia_simulatedData.csv` contains personal, clinical, and other details on
patients diagnosed and treated for certain leukemias. Starting with the "Dx" (diagnosis)
column, what two diseases are represented in the data set? (*Hint*: don't just type
the codes from the data set)

*Type your answer below:*
leukemia_simulatedData = read.csv("~/Week 5/Week5_data/leukemia_simulatedData.csv")
colnames((leukemia_simulatedData))
##Diseases are Chronic myelomonocytic leukemia and Acute myeloblastic leukemia


## Q2 (10 points)

Our goal for this analysis will be to determine whether demographic, clinical,
or genomic factors correlate with response or non-response to therapy. 
Looks like there's quite a bit of PHI and other unnecessary data.

Using R, remove columns containing unnecessary data & PHI from this data set,
and save as a new data frame. *Hint:* We do want to include Age in this analysis, 
but birthdays are too specific.

```{r}
colnames((leukemia_simulatedData))
leukemia_simulatedData <- leukemia_simulatedData [,-c (1,2,3,17,19,20,21)]
leukemia_simulatedData$Birth_Date = as.Date(leukemia_simulatedData$Birth_Date, format = "%m/%d/%Y")
head(leukemia_simulatedData$Birth_Date)
surveyDate = as.Date("1/1/2020", format = "%m/%d/%Y")


leukemia_simulatedData$Age = as.numeric(difftime(surveyDate, leukemia_simulatedData$Birth_Date , units= "days")/365)
leukemia_simulatedData$Age = round(leukemia_simulatedData$Age)
head(leukemia_simulatedData$Age)
head(leukemia_simulatedData)

leukemia_simulatedData = leukemia_simulatedData [ ,-1]
head(leukemia_simulatedData)

```


## Q3 (10  points)

A few of the columns are not consistent, and have multiple values corresponding
to the same thing (Treatment, for example: aza=azacitidine, DAC=decitabine).
table() may help you identify these columns (*Hint:* There are 3 columns that
need cleaning for consistency).

Starting with your result from Q2, clean the data so that columns contain 
consistent values. Also, ensure that columns containing numeric data (like lab 
measurements) are the correct class.

Using write.csv(), save your deidentified & clean table as "leukemia_YourName.csv", 
and submit it along with this Rmd file.


```{r}
str(leukemia_simulatedData)
View(leukemia_simulatedData)

leukemia_simulatedData$Treatment[leukemia_simulatedData$Treatment == "aza"] = "azacitidine"
leukemia_simulatedData$Treatment[leukemia_simulatedData$Treatment == "DAC"] = "decitabine"


leukemia_simulatedData$TP53.Mutation[leukemia_simulatedData$TP53.Mutation == "yes"] = "1"
leukemia_simulatedData$TP53.Mutation[leukemia_simulatedData$TP53.Mutation == "no"] = "0"

leukemia_simulatedData$ASXL1.Mutation [leukemia_simulatedData$ASXL1.Mutation == "no"] = "0"
leukemia_simulatedData$ASXL1.Mutation [leukemia_simulatedData$ASXL1.Mutation == "yes"] = "1"


```


## Bonus (3 points)

Using a loop, program a "guessing game" in R.
  - Game should generate a random integer from 1 to 100 for the answer, but 
    don’t tell the user (the sample() function could help).
  - Ask the user for a guess (use readline()), then say if correct, or if the guess is too high or too low.
  - Continue asking for guesses until correct.  Then tell the user how many guesses it took.
  - Start by using an R script. Use the ‘Source’ button to test your game.

```{r}

# When you're satisfied with your code, copy it here.


```

