---
title: "Homework 2"
author: "Your Name"
date: "7/2/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Problem Set
## Q1 (5 points)

What is the difference between a matrix and a data frame? When might we want to
use a data frame instead of a matrix?

**Type your answer below:**
In a matrix all the data have to be in the same class
In data frame it can have any number of class

Because data frames allow more than one class you can have diverse data points.


## Q2 (5 points) 

Use an R command to find the "needle" in the list below.

```{r}

haystack <- list(hay1 = c("not_here", "or_here"),
                 hay2 = 250:400,
                 hay3 = list(more_numbers = c(55, 44, 33),
                             a_data_frame = data.frame(who = c("Amy", "Bart", "Chip"),
                                                       what = c("party", "food", "needle"),
                                                       when = c(1030, 1200, 1415),
                                                       why = c("why_not", "bored", "tired")),
                             a_word = "homework"
                 ),
                 hay4 = c(FALSE, FALSE, FALSE, FALSE, TRUE))

# Type your code below, using brackets and/or $.  The output should be "needle"
haystack[[3]] [[2]] [3,2]

```


## Q3 (5 points)

Read in the `heart.csv` data set. Using R, answer the following questions:
(a) How many patients are in the data set? 

```{r}
#used import dataset to read in heart.csv data
nrow(heart_data)
```

(b) What class is the `thal` column?

```{r}
class(heart_data$thal)

```

(c) How many of the patients have "nontypical" chest pain?

```{r}
table(heart_data$chest_pain)[3]
```

## Q4 (10 points)

Sometimes a typo or strange entry can mess up your whole data analysis. Read in 
`waiting_room3.csv` and try to make a histogram (`hist()`) to show the distribution
of `Waiting_time`. Did it work?

What `class` is `Waiting_time`? Do you see anything wrong with `Waiting_time`? 
Correct the bad entry using an R command (there are multiple acceptable solutions
for this). Then convert the whole column to another class, and try again to make 
a histogram.

```{r}
#used import data set to read in waiting_room3.csv

(hist(waiting_room3))
# This method (`hist(waiting_room3)`) did not work
class(waiting_room3$Waiting_time)
#class is character some one wrote in "maybe 10" so it became a character
waiting_room3$Waiting_time[8] = "10"

waiting_room3$Waiting_time = as.numeric(waiting_room3$Waiting_time)
hist(waiting_room3$Waiting_time)

```
